---
title: "p8105_hw1_rw2844"
author: "Renjie Wei"
date: "2020/9/11"
output: 
  github_document:
    toc: TRUE
---

```{r setup, include = FALSE}
library(tidyverse)

```

# Problem 1

The chunk below is going to create a data frame comprised of:

* a random sample of size 10 from a standard Normal distribution
* a logical vector indicating whether elements of the sample are greater than 0
* a character vector of length 10
* a factor vector of length 10, with 3 different factor “levels”
```{r set_seed, echo = FALSE, message = FALSE}
set.seed(97)
```

```{r problem_1, collapse=TRUE}

df_1 = tibble(
  vec_norm = rnorm(10),
  vec_logical = vec_norm > 0,
  vec_char = rep("char", each = 10),
  vec_factor = factor(sample(c("low", "mid", "high"), 
                             size = 10, replace = TRUE))
)

df_1

#Try to apply mean() to each variable:
mean(df_1 $ vec_norm)
mean(df_1 $ vec_logical)
mean(df_1 $ vec_char)
mean(df_1 $ vec_factor)
```

The `mean()` function works on:

* `vec_norm`, and the average of `vec_norm` is `r mean(df_1 $ vec_norm)`
* `vec_logical`, and the average of `vec_logical` is `r mean(df_1 $ vec_logical)`

But doesn't work on:

* `vec_char`
* `vec_factor`

So the `mean()` function only works on *numeric* and *logical* variables.

The chunk is going to  convert _logical_, _character_ and _factor_ variables to _numeric_ variables.
```{r to_numeric, eval = FALSE}

as.numeric(df_1$vec_logical)
as.numeric(df_1$vec_char)
as.numeric(df_1$vec_factor)

```

This is the second chunk and I'm going to:

* convert the _logical_ vector to _numeric_, and multiply the random sample by the result
* convert the _logical_ vector to a _factor_, and multiply the random sample by the result
* convert the _logical_ vector to a _factor_ and then convert the result to _numeric_, and multiply the random sample by the result

```{r convert_and_math, collapse = TRUE}
logi_ = df_1$vec_logical
norm_ = df_1$vec_norm

as.numeric(logi_) * (norm_)
as.factor(logi_) * (norm_)
as.numeric(as.factor(logi_)) * (norm_)

```

# Problem 2

```{r setup_penguins}
data("penguins", package = "palmerpenguins")
```

